Rotations and Insecticide Resistance the story

### 2019-03-12 inst/documents/rotations_notes.Rmd
notes

@@

fix error
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 1e-04 , rot_interval = 10 , eff = 0.95 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0.01 , cost = 0.01 , logy = FALSE , no_r_below_start = FALSE , min_rwr_interval = 5 , threshold = 0.9 , mort_or_freq ='mort' )

~ rot_interval > 0
in insecticide_check()
Error in genotype_freq(rfreq) : 
  argument "rfreq" is missing, with no default

~ publish to shinyapps and send link to Ian

@@

@@

~ do I need to be able to plot mortality over time ?
~~ on the same graph as resistance frequency or a different one ?

@@

~ move github repo back to mine
~~ From Github I merged changes from Ians with a pull request after comparing across the forks.
~~ Now I can possibly change RStudio to point to the repo on my Github (do when I have a bit more time)

>>>>

8/3/19
eeek, found that there is a cran package called rotations, and this seems to be messing up deployment to shinyapps
but was OK when I installed my rotations from github

~ published to shinyapps and sent link to Ian

@@

~~ why in this scenario does it rotate insecticides even though it starts below mortality threshold
(to do with min_rwr threshold)
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 1e-04 , rot_interval = 0 , eff = 0.9 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.6 , migration = 0.01 , cost = 0.01 , logy = FALSE , no_r_below_start = FALSE , min_rwr_interval = 5 , threshold = 0.9 , mort_or_freq ='mort' )

~ fix plot error when coverage==1

@@

~ TIDY UP CODE AND IMPROVE DOCUMENTATION e.g. function args

@@

@@
